---
title: "Bayer Large Scale Dicamba Volatility Study"
subtitle: ""
address: University of Wisconsin-Madison
author: "| Rodrigo Werle^1^, Ryan DeWerff^2^, Nick Arneson^3^, Max Oliveira^4^, Sarah Striegel^5^, Victor Ribeiro^5^, Nikola Arsenijevic^5^, Felipe Faleco^5^, Kolby Grint^5^, Haleigh Ortmeier-Clarke^5^ and  Madison Mels^6^ \n| ^1^ Principal
  Investigator\n| ^2^ Research Technician  ^3^ Outreach Research and Extension Associate ^4^ Postdoctoral Research Associate ^5^ Graduate Student ^6^ Undergraduate Research Assistant \n"

# Change the following lines only if you know what you are doing:
#date: '`r format(Sys.Date(), "%d\\. %m\\. %Y")`'  # today
fontfamily: lmodern
fontsize: 12pt
graphics: null
papersize: 
geometry: margin=1.0in
classoption:
  - a4paper
  - oneside
  #- more options here, see rmarkdown documentation 
numbersections: yes
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{booktabs}
- \usepackage{multirow}
- \usepackage{float}
fig_caption: yes
keep_tex: yes
output: pdf_document
---



\newpage 
\tableofcontents 
\newpage 
\listoffigures
\newpage 
\listoftables
\newpage


# Methods

•	Soybean variety:

•	Soybean seed rate: 

•	Soybean row width: 

•	Soybean planting date:

•	PRE-herbicide: 

•	PRE-herbicide application: 

•	Herbicide treatments application (Flat): 

•	Soybean stage at flat application: 

•	Soybean height at flat application: 

•	Flat removal from low-tunnel: 

•	Results presented at 21 DAT (days after treatment)

•	Photos taken at 21 DAT  

\newpage

```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(drc)
```
```{r include=FALSE}
Data <- read_csv("Dicamba.csv") 
glimpse(Data)
```

```{r include=FALSE}
No <- Data %>% 
  filter(Location == "N" | Row != 1) 


N <- drm(Injury ~ Distancem, Type, fct = l3(), data=No)
summary(N)
```


```{r fig.height=6, fig.width=6, warning=FALSE}
plot(N, main="North", sub="University od Wisconsin-Madison Weed Science", xlim=c(0,80), ylim=c(0,100),
     type="average", log="", col=c(1,2),
     cex=1.2, cex.lab=1.5, cex.axis=1.1, pch=c(1,16), lwd=3, xlab="Distance (m)", ylab="Non-DT soybean injury")
```











